Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-28 main.tex
Add updated citation for dojo.
Move back to bibtex.
The biblatex version has been updated on arxiv and this is incompatible
with the default/current texlive version on ubuntu. I struggled and have
given up :)
Prepare manuscript for ECJ.

\documentclass{article}

@@

\usepackage[backend=biber, firstinits=false, backref=false, url=true,
            isbn=true, style=numeric]{biblatex}
\addbibresource{bibliography.bib}

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and
        Vincent Knight \and
        Martin Jones \and
        Georgios Koutsovoulos \and
        Nikoleta E. Glynatsi \and
        Owen Campbell}
\date{}

@@

@@

A total of \input{./assets/number_of_players.tex}are included, of which
\input{./assets/number_of_stochastic_players.tex}are stochastic.  In
Section~\ref{sec:standard} is concerned with the standard tournament with 200
turns whereas in Section~\ref{sec:noise} a tournament with 5\% noise is
discussed. Due to the inherent stochasticity of these IPD tournaments, these
tournament were repeated \input{./assets/standard_number_of_repetitions.tex}
times. This allows for a detailed and confident analysis of the performance of
strategies. To illustrate the results considered,
Figure~\ref{fig:tit_for_tat_scores} shows the distribution of the mean score per
turn of Tit For Tat over all the repetitions. Similarly,
Figure~\ref{fig:tit_for_tat_ranks} shows the ranks of of Tit For Tat for each
repetition (we note that it never wins a tournament). Finally
Figure~\ref{fig:tit_for_tat_wins} shows the number of opponents beaten in any given
tournament: Tit For Tat does not win any match (this is due to the fact that it
will either draw with mutual cooperation or defect second).

@@

As shown in Table~\ref{tbl:noisy_wins_top_winners} and
Figure~\ref{fig:noisy_winplot} the strategies tallying the most wins are
somewhat similar to the standard tournaments, with Defector, the handshaking
CollectiveStrategy~\cite{Li2009}, and Aggravate appearing as the top three again.

@@

All implementations of these algorithms are archived at
\cite{marc_harper_2017_824264}. This software is (similarly to the Axelrod
library) available on github
\url{https://github.com/Axelrod-Python/axelrod-dojo}. There are objective
functions for:

@@

\printbibliography

>>>>

\documentclass{article}
\usepackage{ecj,palatino,epsfig,latexsym,natbib}

@@

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
       Iterated Prisoner's Dilemma}

\author{
		\name{\bf Marc Harper} \hfill \addr{marcharper@gmail.com}\\
        \addr{Google Inc., Mountain View, CA, USA}
\AND
		\name{\bf Vincent Knight} \hfill \addr{knightva@cardiff.ac.uk}\\
        \addr{Cardiff University, School of Mathematics, UK}
\AND
		\name{\bf Martin Jones} \hfill \addr{martin@pythonforbiologists.com}\\
        \addr{Not affiliated}
\AND
		\name{\bf Georgios Koutsovoulos} \hfill \addr{georgios.koutsovoulos@inra.fr}\\
        \addr{INRA, Université Côte d‘Azur, CNRS, ISA, France}
\AND
		\name{\bf Nikoleta E. Glynatsi} \hfill \addr{glynatsiNE@cardiff.ac.uk}\\
        \addr{Cardiff University, School of Mathematics, UK}
\AND
		\name{\bf Owen Campbell} \hfill \addr{owen.campbell@tanti.org.uk}\\
        \addr{Not affiliated}
}
\date{}

@@

\begin{keywords}
    Game Theory,
    Genetic algorithms,
    Prisoners dilemma,
\end{keywords}

@@

A total of \input{./assets/number_of_players.tex}are included, of which
\input{./assets/number_of_stochastic_players.tex}are stochastic.
Section~\ref{sec:standard} is concerned with the standard tournament with 200
turns whereas in Section~\ref{sec:noise} a tournament with 5\% noise is
discussed. Due to the inherent stochasticity of these IPD tournaments, these
tournaments were repeated \input{./assets/standard_number_of_repetitions.tex}
times. This allows for a detailed and confident analysis of the performance of
strategies. To illustrate the results considered,
Figure~\ref{fig:tit_for_tat_scores} shows the distribution of the mean score per
turn of Tit For Tat over all the repetitions. Similarly,
Figure~\ref{fig:tit_for_tat_ranks} shows the ranks of of Tit For Tat for each
repetition. (We note that it never wins a tournament). Finally
Figure~\ref{fig:tit_for_tat_wins} shows the number of opponents beaten in any given
tournament: Tit For Tat does not win any match. (This is due to the fact that it
will either draw with mutual cooperation or defect second).

@@

As shown in Table~\ref{tbl:noisy_wins_top_winners} and
Figure~\ref{fig:noisy_winplot} the strategies tallying the most wins are
somewhat similar to the standard tournaments, with Defector, the handshaking
CollectiveStrategy~\cite{Li2009}, and Aggravater appearing as the top three again.

@@

All implementations of these algorithms are archived at
\cite{dojo}. This software is (similarly to the Axelrod
library) available on github
\url{https://github.com/Axelrod-Python/axelrod-dojo}. There are objective
functions for:

@@

\bibliographystyle{plain}
\bibliography{bibliography.bib}
